---
output: github_document
---


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tinylens

<!-- badges: start -->
[![R-CMD-check](https://github.com/arbelt/tinylens/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/arbelt/tinylens/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of tinylens is to provide a minimal set of tools for working with lenses in R. 

As of the initial release, this is basically a re-implementation of the `lenses` package (https://github.com/cfhamill/lenses).

## Installation

You can install the development version of tinylens from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("arbelt/tinylens")
```

## Example

The main benefit of lenses is that they are composable, and so allow for more streamlined transformations of nested data structures.

```{r example}
library(tinylens)
## basic example code
```
